```{r}

academy <- read.csv("c:/r/academy.csv", header=T, stringsAsFactors=F )
academy
academy2 <- academy[ , c(3,4)] 
academy2
plot(academy2)

#install.packages("factoextra")
library(factoextra)

km <- kmeans(academy2, 4)

fviz_cluster(km, data = academy2,
             stand=F, 
             ellipse.type = "t")


#install.packages("tripack")

library(tripack)
library(RColorBrewer)

color <- brewer.pal(4, "Pastel1")
academy_V <- voronoi.mosaic(km$centers[,1], km$centers[,2])
academy_P <- voronoi.polygons(academy_V)
plot(academy2, pch = 19, col = color[km$cluster])
points(km$centers[,1], km$centers[,2], pch =3, cex = 1.5, lwd=2)
plot(academy_V, add = T)



```

[문제229] 영어와 수학점수로 크게 4개의 그룹의 학생집합으로 분류하세요


academy <- read.csv("c:/r/academy.csv", header=T, stringsAsFactors=F )
academy2 <- academy[ , c(3,4)] 
academy2
plot(academy2)

install.packages("factoextra")
library(factoextra)

km <- kmeans(academy2, 4)

fviz_cluster(km, data = academy2,
             stand=F, 
             ellipse.type = "t")


install.packages("tripack")

library(tripack)
library(RColorBrewer)

color <- brewer.pal(4, "Pastel1")
academy_V <- voronoi.mosaic(km$centers[,1], km$centers[,2])
academy_P <- voronoi.polygons(academy_V)
plot(academy2, pch = 19, col = color[km$cluster])
points(km$centers[,1], km$centers[,2], pch =3, cex = 1.5, lwd=2)
plot(academy_V, add = T)

```{r}

```


