```{r}
x<- 6
y<- 6
data<- x*y
data1<- c(1:data)
data1

for(i in c(1:x)){
  
}


matrix(data = 0,nrow=x,ncol=y,byrow=T)

data<- c(1:30)
data[1:6]
data[7:]




ma01<- function(a,b){
  
  x<- c(1:a)
  y<- c(1:b)
  
  x1<- NULL
  if(length(x)%% 2 ==0){
    x1<- NULL
    for(i in 0:((length(x)/2)-1 )){
      x1<- append(x1,x[1+i])
      x1<- append(x1,x[length(x)-i])
    }
  } else{
    x1<- NULL
    for(i in 0:((length(x)/2)-0.5 )){
      x1<- append(x1,x[1+i])
      x1<- append(x1,x[length(x)-i])
    }
    x1<- x1[-length(x1)]
  }
    
  y1<- NULL
  if(length(y)%% 2 ==0){
    y1<- NULL
    for(i in 0:((length(y)/2)-1 )){
      y1<- append(y1,y[length(y)-i])
      y1<- append(y1,y[1+i])
    }
  } else{
    y1<- NULL
    for(i in 0:((length(y)/2)-0.5 )){
      y1<- append(y1,y[length(y)-i])
      y1<- append(y1,y[1+i])
    }
    y1<- y1[-length(y1)]
  }

  data<- c(1:a*b)
  data1<- matrix(NA,nrow=a,ncol=b,byrow = T)

  x2<- c((a-1):0)
  y2<- c(b:0)
  
  t1<- 1
  t2<- y2[1]
  
  for ( i in (ifelse((length(x) >= length(y))==TRUE, 1:length(y), 1:(length(x)-1))){
    
    
    data1[x1[i*2-1],is.na(data1[x1[i*2-1],])]<- data[t1:t2]
    
    t1<- t1+y2[#2]   i*4-i*3
    t2<- t2+y2[#2]
    
        data1[is.na(data1[,y1[i*2-1]]),y1[i*2-1]]<- data[t1,t2]
    
    t1<- t1+y2[#3]   1*5-i*2
    t2<- t2+y2[#3]
    
    data1[x1[i*2],is.na(data1[x1[i*2],])]<- sort(data[t1:t2],decreasing=T)
    
    t1<- t1+y2[#4]    i*5-i*1
    t2<- t2+y2[#4]
      
    data1[is.na(data1[,y1[i*2]]),y1[i*2]]<- sort(data[t1:t2],decreasing=T)
    
    t1<- t1+y2[#5]    i*5
    t2<- t2+y2[#5]
    
  }
data1
    for(i in 1:length(x1/2)){
    
  }
  
  for(i in 1:length(x1)/2){
    for(j in 1:length(y1)/2){
      data1[x1[i*2-1],is.na(data1[x1[i*2-1],])]<- data[1:5]
      
      data1[is.na(data1[,y1[i*2-1]]),y1[i*2-1]]<- data[6:10]
      
      data1[x1[i*2],is.na(data1[x1[i*2],])]<- sort(data[11:14],decreasing=T)
      
      data1[is.na(data1[,y1[i*2]]),y1[i*2]]<- sort(data[15:18],decreasing=T)
      
      data1[2,data1[2,]==0]<- data[19:21]
      
      data1[data1[,4]==0,4]<- data[22:24]
      
      data1[5,data1[5,]==0]<- sort(data[25:26],decreasing=T)
      
      data1[data1[,2]==0,2]<- sort(data[27:28],decreasing=T)
      
      data1[3,data1[3,]==0]<- data[29:29]
      
      data1[data1[,3]==0,3]<- sort(data[30:30],decreasing=T)
        
        
  
  
}

ma01(10,10)

data1<- matrix(0, nrow= 6,ncol = 5,byrow=T)

data1[1,]<- data[1:5]

data1[data1[,5]==0,5]<- data[6:10]

data1[6,data1[6,]==0]<- sort(data[11:14],decreasing=T)

data1[data1[,1]==0,1]<- sort(data[15:18],decreasing=T)

data1[2,data1[2,]==0]<- data[19:21]

data1[data1[,4]==0,4]<- data[22:24]

data1[5,data1[5,]==0]<- sort(data[25:26],decreasing=T)

data1[data1[,2]==0,2]<- sort(data[27:28],decreasing=T)

data1[3,data1[3,]==0]<- data[29:29]

data1[data1[,3]==0,3]<- sort(data[30:30],decreasing=T)

```

문제는 다음과 같다:

6 6

  0   1   2   3   4   5
 19  20  21  22  23   6
 18  31  32  33  24   7
 17  30  35  34  25   8
 16  29  28  27  26   9
 15  14  13  12  11  10
위처럼 6 6이라는 입력을 주면 6 X 6 매트릭스에 나선형 회전을 한 값을 출력해야 한다.


data<- c(1:30)
data[1:5] 5
data[6:10] 6-1
data[11:14] 5-1
data[15:18] 6-2
data[19:21] 5-2
data[22:24] 6-3
data[25:26] 5-3
data[27:28] 6-4
data[29:29] 5-4
data[30:30] 6-5


data1<- matrix(data = c(1:30), nrow= 6,ncol = 5,byrow=T)
data1



data1[1,]<- data[1:5]

data1[,5][-1]<- data[6:10]

data1[6,][-5]<- sort(data[11:14],decreasing=T)

data1[,1][c(-1,-6)]<- sort(data[15:18],decreasing=T)

data1[2,][c(-5,-1)]<- data[19:21]

data1[,4][c(-1,-6,-2)]<- data[22:24]

data1[5,][c(-5,-1,-4)]<- sort(data[25:26],decreasing=T)

data1[,2][c(-1,-6,-2,-5)]<- sort(data[27:28],decreasing=T)

data1[3,][c(-5,-1,-4,-2)]<- data[29:29]

data1[,3][c(-1,-6,-2,-5,-3)]<- sort(data[30:30],decreasing=T)



data1[1,]<- data[1:5]

data1[6,][-5]<- sort(data[11:14],decreasing=T)

data1[2,][c(-5,-1)]<- data[19:21]

data1[5,][c(-5,-1,-4)]<- sort(data[25:26],decreasing=T)

data1[3,][c(-5,-1,-4,-2)]<- data[29:29]




data1[,5][-1]<- data[6:10]

data1[,1][c(-1,-6)]<- sort(data[15:18],decreasing=T)

data1[,4][c(-1,-6,-2)]<- data[22:24]

data1[,2][c(-1,-6,-2,-5)]<- sort(data[27:28],decreasing=T)

data1[,3][c(-1,-6,-2,-5,-3)]<- sort(data[30:30],decreasing=T)









```{r}
  x<- c(1:6)
  y<- c(1:5)
  
  x1<- NULL
  if(length(x)%% 2 ==0){
    x1<- NULL
    for(i in 0:((length(x)/2)-1 )){
      x1<- append(x1,x[1+i])
      x1<- append(x1,x[length(x)-i])
    }
  } else{
    x1<- NULL
    for(i in 0:((length(x)/2)-0.5 )){
      x1<- append(x1,x[1+i])
      x1<- append(x1,x[length(x)-i])
    }
    x1<- x1[-length(x1)]
  }
    
  y1<- NULL
  if(length(y)%% 2 ==0){
    y1<- NULL
    for(i in 0:((length(y)/2)-1 )){
      y1<- append(y1,y[length(y)-i])
      y1<- append(y1,y[1+i])
    }
  } else{
    y1<- NULL
    for(i in 0:((length(y)/2)-0.5 )){
      y1<- append(y1,y[length(y)-i])
      y1<- append(y1,y[1+i])
    }
    y1<- y1[-length(y1)]
  }
x1
y1


data<- c(1:(6*5))
data
data1<- matrix(NA, nrow= 6,ncol = 5,byrow=T)
data1

x2<- c((6-1):0)
y2<- c(5:0)

x2
y2

t<- y2[1]

data1[1,]<- data[length(data1[1,])-t+1:t]

t<- t + x2[1]
t2<- length(data1[1,])-t+1

data1[data1[,5]==0,5]<- data[6:t]

t<- t + y2[2]

data1[6,data1[6,]==0]<- sort(data[11:t],decreasing=T)

t<- t+ x2[2]

data1[data1[,1]==0,1]<- sort(data[15:t],decreasing=T)

data1[2,data1[2,]==0]<- data[19:21]

data1[data1[,4]==0,4]<- data[22:24]

data1[5,data1[5,]==0]<- sort(data[25:26],decreasing=T)

data1[data1[,2]==0,2]<- sort(data[27:28],decreasing=T)

data1[3,data1[3,]==0]<- data[29:29]

data1[data1[,3]==0,3]<- sort(data[30:30],decreasing=T)

```














